\textit{Two Foraging Algorithms for Robot Swarms Using Only Local Communication}~\cite{hoff2010two} \\

The authors present two algorithms, when foraging for food, which allows coordination between robots, but don't require physical environmental marks such as pheramones. The two algorithms proposed, $Virtual~Pheromones$ and the $Cardinality~Algorithm$, both arrange the robots into a dual class system of $walkers$ and $beacons$ and return two values based on relations to resource and the nest, but differ in the value assigned to each $beacon$. The first has the agents leave the nest, then begins to classify $beacons$ adhoc. Floating point values are assigned to each beacon, with a constant decay rate, where rewards are given to $beacons$ that are within range of $walkers$, thus creating a trail to the robot with the highest $virtual~pheromone$ value.  $Cardinality$ differs in that it doesn't calculate pheromone trails but counts the number of beacons within range between itself and the resource or the nest. These approaches were compared against a random walking algorithm and a food GPS algorithm that knows the location of resources and the nest alike, which creates a lower and upper bound for their experiments. They found that the $cardinality~algorithm$ outperformed the $virtual~pheromone$ in both obstacle and obstacle-free cases with a much higher food return rate and quicker model stabalization over fewer time steps. These algorithms were also scalable to an extent, but when the number of rovers exceeded 100, congestion was created around resources and the nest.

This article presents an interesting approach to foraging for materials, using the swarm as a whole to search larger areas. Although not directly specific to project, the rovers will need some type of foraging control algorithm that governs their trajectories. I can use this style of searching and path plotting between resource and nest within my project. Not explicitly discussed in the summary, but an interesting aside was their conclusion that two separate paths that share only goal and resource endpoints, was needed to eleviate head-on rover collusions when transporting food. I had a similar idea that had the rovers travel along directional arc that were equivalent, but rotated by $\frac{\pi}{2}$, that would lay between resource and home. This is similar to how a highway is setup.